\huge Risk of non-Hodgkin lymphoma under hypothetical interventions with guaranteed positivity

### 2023-06-12 reports/SER (2023)/resources/intervention-density-combo2.tex
SER postr

% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:29
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48,144.82);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 80.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 48.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 80.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (133.29, 48.84) rectangle (141.37, 80.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 80.84);

@@

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (197.94, 48.84) rectangle (206.02, 80.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (238.35, 48.84) rectangle (246.43, 80.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21,208.81);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 81.74) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,117.73) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,153.72) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,189.72) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 84.84) --
	( 33.90, 84.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,120.83) --
	( 33.90,120.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,156.82) --
	( 33.90,156.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,192.81) --
	( 33.90,192.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-06-02 02:14:31
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 44.40, 48.84) rectangle ( 52.48, 48.84);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 52.48, 48.84) rectangle ( 60.56, 94.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 60.56, 48.84) rectangle ( 68.64,105.98);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 68.64, 48.84) rectangle ( 76.73, 71.70);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] ( 84.81, 48.84) rectangle ( 92.89, 71.70);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 94.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13, 71.70);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 48.84);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (141.37, 48.84) rectangle (149.45, 83.12);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (149.45, 48.84) rectangle (157.54, 71.70);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (165.62, 48.84) rectangle (173.70, 60.27);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (173.70, 48.84) rectangle (181.78, 60.27);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (181.78, 48.84) rectangle (189.86, 60.27);

@@

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (214.10, 48.84) rectangle (222.18, 60.27);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (222.18, 48.84) rectangle (230.26, 60.27);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (230.26, 48.84) rectangle (238.35, 71.70);

@@

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (100.97, 48.84) rectangle (109.05, 94.55);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (109.05, 48.84) rectangle (117.13,208.81);

\path[draw=drawColor,line width= 1.6pt,fill=fillColor,fill opacity=0.20] (117.13, 48.84) rectangle (125.21, 48.84);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95, 90.02) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,134.30) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 28.95,178.58) {15};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15, 93.12) --
	( 33.90, 93.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,137.40) --
	( 33.90,137.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.15,181.67) --
	( 33.90,181.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,216.81);
\definecolor{drawColor}{gray}{0.20}
